GO enrichment

### 2021-12-20 analysis/GOenrichment.Rmd
add tables

  names(dat) <- c("term_ID","description","frequency", 'plot_X', 'plot_Y', 'log_size', 'value', 'uniqueness', 'dispensability', 'eliminated', 'representative')
  one.data <- dat
  if (one.data[1,] == '<html>') {next} # some datasets result in error
  one.data <- one.data [(one.data$plot_X != "null" & one.data$plot_Y != "null") & (! is.na(one.data$frequency)) & (one.data$value != 'null'), ];
  one.data <- type_convert(one.data)

  p1 <-
    ggplot(data = one.data, aes(plot_X, plot_Y, label = description)) +
    geom_point(aes(colour = value, size = log_size), alpha = I(0.6)) +
    scale_size_area() +
    scale_colour_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")), 
                           limits = c(min(one.data$value), 0)) +
    geom_point(
      aes(plot_X, plot_Y, size = log_size),
      shape = 21,
      fill = "transparent",
      colour = I (alpha ("black", 0.6))
    ) +
    scale_size_area() +
    geom_label_repel(max.overlaps = 5, box.padding = 0.5,
                     aes(point.size = log_size)) +
    theme_minimal() +
    labs(y = "Semantic space x",
         x = "Semantic space y",
         color = 'Log(p-value)',
         size = 'Frequency') +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank()
    ) +
    ggtitle(f)

@@

@@

Let's have a look at all of these plots. Manually zooming in leads to ggrepel reloading labels, so on the small scale a lot of these plots don't have labels.
```{r}
plot_list
```

>>>>

  names(dat) <- c("term_ID","description","frequency", 'plot_X', 'plot_Y', 'log_size', 'value', 'uniqueness', 'dispensability', 'eliminated', 'representative')
  one.data <- dat
  if (one.data[1,] == '<html>') {next} # some datasets result in error
  one.data <- one.data [(one.data$plot_X != "null" & one.data$plot_Y != "null") & (! is.na(one.data$frequency)) & (one.data$value != 'null'), ];
  one.data <- type_convert(one.data)
  top_ten_values <- one.data %>% arrange(value) %>% head(10) %>% pull(term_ID) 
  one.data <- one.data %>% mutate(description2 = case_when(
    term_ID %in% top_ten_values ~ description, 
                                                           TRUE ~ ''))
  p1 <-
    ggplot(data = one.data, aes(plot_X, plot_Y, label = description2)) +
    geom_point(aes(colour = value, size = log_size), alpha = I(0.6)) +
    scale_size_area() +
    scale_colour_gradientn(colours = rev(wes_palette("Zissou1", 100, type = "continuous")), 
                           limits = c(min(one.data$value), 0)) +
    geom_point(
      aes(plot_X, plot_Y, size = log_size),
      shape = 21,
      fill = "transparent",
      colour = I (alpha ("black", 0.6))
    ) +
    scale_size_area() +
    geom_label_repel(max.overlaps = Inf, box.padding = 0.5,
                     aes(point.size = log_size)) +
    theme_minimal() +
    labs(y = "Semantic space x",
         x = "Semantic space y",
         color = 'Log(p-value)',
         size = 'Frequency') +
    theme(
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank()
    ) +
    NULL
    #ggtitle(f)

@@

# Making Supplementary Tables for the REVIGO results

Let's also pull these terms out as tables

```{r}
for( i in names(results_list)) {
  print(i)
  knitr::kable(results_list[[i]] %>% filter(Eliminated == FALSE), label=i)
}

@@

Let's have a look at all of these plots. Manually zooming in leads to ggrepel reloading labels, so on the small scale a lot of these plots don't have labels.
```{r}
for(i in names(plot_list)) {
  file_name = paste('output/',  i, '.png', sep='')

  cowplot::save_plot(file_name, plot_list[[i]], base_height=8)
